Evolutionary stretegies

### 2015-12-17 evolutionaryComputation/notes4.tex
added some lecture notes

Try to keep the fitness function simple.
\end{document}

>>>>

Try to keep the fitness function simple.

\section{Model GA}
Learn structure from good solutions.
Is very broad applicable because few assumptions.

Probability model is a vector(1,0,0.5)
Where 0.5 = random,
0 = 100 percent certainty of 0
1 = 100 percent certainty of 1

Overfitting, you don't learn anything because you
made it perfect.

deception is the problem, not non lineararity.

\section{PMGA}
Modelling baysion networks you should look at the fitting of data *and* model
complexity

Foss can be anything, for example:
  3456
0110110
1234

with the first and alst row being indeci of subsets.

univariate is just one big set.
marginal product = Mutex set
Hiercial tree, multiple level of linkage, the bottom no linkage the top 
uniform and marginal product in between in varying levels.

mutual information is super important concept\ldots

\end{document}
